Cross-validation of regression models: mixed model examples (edited v3)

### 2024-07-29 scratch/JSS-submission/Fox-Monette-cv-package.Rmd
tweak edit to JSS paper

To compute cross-validated fitted values when the folds contain more than one case, we make use of the Woodbury matrix identity [@Hager:1989],
$$
\left(\mathbf{A}_{m \times m} + \mathbf{U}_{m \times k} 
\mathbf{C}_{k \times k} \mathbf{V}_{k \times m} \right)^{-1} = \mathbf{A}^{-1} - \mathbf{A}^{-1}\mathbf{U} \left(\mathbf{C}^{-1} + 
\mathbf{VA}^{-1}\mathbf{U} \right)^{-1} \mathbf{VA}^{-1}
$$
where $\mathbf{A}$ is a nonsingular order-$m$ matrix. We apply this result by letting
\begin{align*}
	\mathbf{A} &= \mathbf{X}^\top \mathbf{W} \mathbf{X} \\
	\mathbf{U} &= \mathbf{X}_\mathbf{j}^\top \\
	\mathbf{V} &= - \mathbf{X}_\mathbf{j} \\
	\mathbf{C} &= \mathbf{W}_\mathbf{j} \\
\end{align*}
where the subscript $\mathbf{j} = (i_{j1}, \ldots, i_{jn_j})^\top$ represents the vector of indices for the $n_j \approx n/k$ cases in the $j$th fold, $j = 1, \ldots, k$. The negative sign in $\mathbf{V} = - \mathbf{X}_\mathbf{j}$ reflects the *removal*, rather than addition, of the cases in $\mathbf{j}$.

>>>>

To compute cross-validated fitted values when the folds contain more than one case, we make use of the Woodbury matrix identity [@Hager:1989],
$$
\left(\mathbf{A}_{m \times m} + \mathbf{U}_{m \times k} 
\mathbf{C}_{k \times k} \mathbf{V}_{k \times m} \right)^{-1} = \mathbf{A}^{-1} - \mathbf{A}^{-1}\mathbf{U} \left(\mathbf{C}^{-1} + 
\mathbf{VA}^{-1}\mathbf{U} \right)^{-1} \mathbf{VA}^{-1}
$$
where $\mathbf{A}$ is a nonsingular order-$m$ matrix. We apply this result by letting
\begin{align*}
	\mathbf{A} &= \mathbf{X}^\top \mathbf{W} \mathbf{X} \\
	\mathbf{U} &= \mathbf{X}_\mathbf{j}^\top \\
	\mathbf{V} &= - \mathbf{X}_\mathbf{j} \\
	\mathbf{C} &= \mathbf{W}_\mathbf{j} \\
\end{align*}
where the subscript $\mathbf{j} = (i_{j1}, \ldots, i_{jm})^\top$ represents the vector of indices for the $m = n_j \approx n/k$ cases in the $j$th fold. The negative sign in $\mathbf{V} = - \mathbf{X}_\mathbf{j}$ reflects the *removal*, rather than addition, of the cases in $\mathbf{j}$.
